A Loop Quantum Gravity Inspired Action for the Bosonic String and Emergent Dimensions at Large Scales

### 2025-08-27 lqg-strings.tex
corrected the equations in sec 3B missing the f's, clarified the importance of the equation describing the KR pullback and justified the area corrected KR action

	\left( \delta _{a} ^{c'} \delta _{b} ^{d'} H_{\mu \nu} - \frac{1}{2 g} \Delta _{a c} \varepsilon ^{c c'} \Delta _{b d} \varepsilon ^{d d'} G_{\mu \nu} \right) \times \\

@@

	H_{\mu \nu} = \frac{\Delta}{2 g} G_{\mu \nu} .

@@

If one were to calculate the equations of motion for the quantum of area field $\Delta _{a b}$ in the actions \eqref{eqn:modified-ng-action} and \eqref{eqn:inverse-metric-Polyakov} explored before, one would end up concluding that either $\Delta _{a b} = 0$ or it's determinant $\Delta = 0$ vanish. This happens because, as we explored in section \ref{sec:ws-kalb-ramond}, $\Delta _{a b}$ is actually related to the pullback of the Kalb-Ramond field $B_{\mu \nu}$, but those actions were actions for the free string, not coupled to said field. The more complete picture would be thus to consider the (area-corrected) string now coupled to the Kalb-Ramond field \cite{Tong2009Lectures}
\begin{multline} \label{eqn:area-corrected-K-R-action}
	S = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) \times \\
	\times \Big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \varepsilon ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Big),
\end{multline}
where  we can rewrite $\varepsilon ^{a b}$ in terms of $\Delta ^{a b}$ as
\begin{multline} \label{eqn:area-corrected-K-R-action-v2}
	S = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) \times \\
	\times \Big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
	- \sqrt{\Delta} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Big) .
\end{multline}
By varying this action \wrt $\Delta ^{c d}$ we get
\begin{equation} \label{eqn:Delta-pullback}
	\Delta _{c d} = \widetilde{f} \del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu}
\end{equation}
with $\widetilde{f}$ given by
\begin{multline} \label{eqn:1/f-tilde}
	\frac{1}{\widetilde{f}} = \frac{1}{g + \dfrac{k \Delta}{2}} \Bigg( \frac{k \sqrt{\Delta}}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
	- \left( g + \frac{3 k \Delta}{4} \right) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigg),
\end{multline}
where if we take $g_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}$ and $\del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} = \Delta _{a b} / \widetilde{f}$ this simplifies to
\begin{equation} \label{eqn:f-tilde}
	\widetilde{f} = - \frac{g + k \Delta}{k \sqrt{\Delta}},
\end{equation}
from which it is easy to see that the pullback of the Kalb-Ramond field $b_{a b} := \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu}$ is given by
\begin{equation} \label{eqn:WS-b-field}
	b_{a b} = - \frac{1}{\dfrac{g}{k \Delta} + 1} \varepsilon _{a b},
\end{equation}
or equivalently that the relation between $\Delta _{a b}$ and $b_{a b}$ is
\begin{equation} \label{eqn:Delta-b-relation}
	\Delta _{a b} = \sqrt{\Delta} \varepsilon _{a b} = - \sqrt{\Delta} \left( \frac{g}{k \Delta} + 1 \right) b_{a b} .
\end{equation}
We thus see that the pullback of the Kalb-Ramond field is actually a tensor \emph{density} of weight $- 1$, since the coefficient in eq \eqref{eqn:WS-b-field} is a true scalar and the Levi-Civita symbol is itself a density.

@@

We start from the action in \eqref{eqn:area-corrected-K-R-action-v2} which describes the area-corrected string coupled to the Kalb-Ramond field, where the Levi-Civita tensor $\varepsilon ^{a b}$ has been written in terms of the quantum of area 2-form $\Delta _{a b}$ by dividing and multiplying by $\sqrt{\Delta}$. Varying this action \wrt \ $\Delta ^{c d}$ yields
\begin{multline} \label{eqn:var-act-AC-KR}
	\frac{\delta S}{\delta \Delta ^{c d}} = - \frac{1}{4 \pi \alpha '} \Bigg( - \frac{1}{2} \frac{k}{\sqrt{- g}} \Delta \Delta _{c d} \bigg( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
	- \sqrt{\Delta} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \bigg) - \\
	- \bigg( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \bigg) \bigg( \frac{1}{2} \sqrt{\Delta} \Delta _{c d} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} + \\
	+ \sqrt{\Delta} \delta ^{a} _{c} \delta ^{b} _{d} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \bigg) \Bigg) ,
\end{multline}
which when required to vanish can be rearranged into
\begin{multline} \label{eqn:eqn:var-act-AC-KR-rear}
	\Delta _{c d} \Bigg( \frac{k \sqrt{\Delta}}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
	- \bigg( g + \frac{3 k \Delta}{4} \bigg) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigg) - \\
	- \bigg( g + \frac{k \Delta}{2} \bigg) \del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu} = 0 .
\end{multline}
From here, the quantum of area field $\Delta _{c d}$ can be directly related to the pullback of the Kalb-Ramond 2-form $\del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu}$ as in
\begin{equation} \label{eqn:QA-pullKR}
	\Delta _{c d} = \widetilde{f} \del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu} ,
\end{equation}
where the function $\widetilde{f}$ is given by a contribution from the pullback of the metric and from the Kalb-Ramond field
\begin{multline} \label{eqn:1/f-KR}
	\frac{1}{\widetilde{f}} = \frac{1}{g + \dfrac{k \Delta}{2}} \Bigg( \frac{k \Delta}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
	- \bigg( g + \frac{3 k \Delta}{4} \bigg) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigg) .
\end{multline}
When the equation of motion for the metric $g_{a b}$ is satisfied i.e if $g_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}$, then \eqref{eqn:1/f-KR} simplifies to
\begin{equation} \label{eqn:1/f-KR-simp}
	\frac{1}{\widetilde{f}} = - \frac{k \sqrt{\Delta}}{g + k \Delta}
\end{equation}
or alternatively
\begin{equation} \label{eqn:f-KR-simp}
	\widetilde{f} = - \frac{g + k \Delta}{k \sqrt{\Delta}} = - \sqrt{\Delta} \left( \frac{g}{k \Delta} + 1 \right) .
\end{equation}
Finally, we can then write the quantum of area 2-form $\Delta _{a b}$ in terms of the pullback of the Kalb-Ramond field $b_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu}$ as
\begin{equation} \label{eqn:QA-KR-fin}
	\Delta _{a b} = - \sqrt{\Delta} \left( \frac{g}{k \Delta} + 1 \right) b_{a b} .
\end{equation}

>>>>

	\left( f^{(H)} \delta _{a} ^{c'} \delta _{b} ^{d'} H_{\mu \nu} - \frac{1}{2 g} f^{(G)} \Delta _{a c} \varepsilon ^{c c'} \Delta _{b d} \varepsilon ^{d d'} G_{\mu \nu} \right) \times \\

@@

	H_{\mu \nu} = \frac{f^{(G)}}{f^{(H)}} \frac{\Delta}{2 g} G_{\mu \nu} .

@@

If one were to calculate the equations of motion for the quantum of area field $\Delta _{a b}$ in the actions \eqref{eqn:modified-ng-action} and \eqref{eqn:inverse-metric-Polyakov} explored before, one would end up concluding that either $\Delta _{a b} = 0$ or it's determinant $\Delta = 0$ vanish. This happens because, as we explored in section \ref{sec:ws-kalb-ramond}, $\Delta _{a b}$ should be related to the pullback of the Kalb-Ramond field $B_{\mu \nu}$, but the actions discussed were actions for the free string, not coupled to said field. The more complete picture would be thus to consider the (area-corrected) string now coupled to the Kalb-Ramond field \cite{Tong2009Lectures}, since this represents the more general and complete diffeomorphism invariant action in $1+1$ dimensions:
\begin{multline} \label{eqn:area-corrected-K-R-action}
	S = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) \times \\
	\times \Big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \varepsilon ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Big),
\end{multline}
where  we can rewrite $\varepsilon ^{a b}$ in terms of $\Delta ^{a b}$ as
\begin{multline} \label{eqn:area-corrected-K-R-action-v2}
	S = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) \times \\
	\times \Big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
	- \sqrt{\Delta} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Big) .
\end{multline}
By varying this action \wrt $\Delta ^{c d}$ we get
\begin{equation} \label{eqn:Delta-pullback}
	\Delta _{c d} = \widetilde{f} \del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu}
\end{equation}
with $\widetilde{f}$ given by
\begin{multline} \label{eqn:1/f-tilde}
	\frac{1}{\widetilde{f}} = \frac{1}{g + \dfrac{k \Delta}{2}} \Bigg( \frac{k \sqrt{\Delta}}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
	- \left( g + \frac{3 k \Delta}{4} \right) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigg),
\end{multline}
where if we take $g_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}$ and $\del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} = \Delta _{a b} / \widetilde{f}$ this simplifies to
\begin{equation} \label{eqn:f-tilde}
	\widetilde{f} = - \frac{g + k \Delta}{k \sqrt{\Delta}},
\end{equation}
from which we can find the pullback of the Kalb-Ramond field $b_{a b} := \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu}$ given in terms of the worldsheet metric $g$ and the quantum of area density $\Delta$ 
\begin{equation} \label{eqn:WS-b-field}
	b_{a b} = - \frac{1}{\dfrac{g}{k \Delta} + 1} \varepsilon _{a b},
\end{equation}
or equivalently that the relation between $\Delta _{a b}$ and $b_{a b}$ is
\begin{equation} \label{eqn:Delta-b-relation}
	\Delta _{a b} = \sqrt{\Delta} \varepsilon _{a b} = - \sqrt{\Delta} \left( \frac{g}{k \Delta} + 1 \right) b_{a b} .
\end{equation}
We thus see that the pullback of the Kalb-Ramond field is actually a tensor \emph{density} of weight $- 1$, since the coefficient in eq \eqref{eqn:WS-b-field} is a true scalar and the Levi-Civita symbol is itself a density.

@@

We start from the action in \eqref{eqn:area-corrected-K-R-action-v2} which describes the area-corrected string coupled to the Kalb-Ramond field, since this is the most generic and complete 2-dimensional action with worldsheet diffeomorphism invariance and bulk global Lorentz symmetry, with the correction to the worldsheet geometry due to quantum geometry proposed by our central dogma. The Levi-Civita tensor $\varepsilon ^{a b}$ has been written in terms of the quantum of area 2-form $\Delta _{a b}$ by dividing and multiplying by $\sqrt{\Delta}$. Varying this action \wrt \ $\Delta ^{c d}$ yields
\begin{multline} \label{eqn:var-act-AC-KR}
	\frac{\delta S}{\delta \Delta ^{c d}} = - \frac{1}{4 \pi \alpha '} \Bigg( - \frac{1}{2} \frac{k}{\sqrt{- g}} \Delta \Delta _{c d} \bigg( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
	- \sqrt{\Delta} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \bigg) - \\
	- \bigg( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \bigg) \bigg( \frac{1}{2} \sqrt{\Delta} \Delta _{c d} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} + \\
	+ \sqrt{\Delta} \delta ^{a} _{c} \delta ^{b} _{d} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \bigg) \Bigg) ,
\end{multline}
which when required to vanish can be rearranged into
\begin{multline} \label{eqn:eqn:var-act-AC-KR-rear}
	\Delta _{c d} \Bigg( \frac{k \sqrt{\Delta}}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
	- \bigg( g + \frac{3 k \Delta}{4} \bigg) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigg) - \\
	- \bigg( g + \frac{k \Delta}{2} \bigg) \del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu} = 0 .
\end{multline}
From here, the quantum of area field $\Delta _{c d}$ can be directly related to the pullback of the Kalb-Ramond 2-form $\del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu}$ as in
\begin{equation} \label{eqn:QA-pullKR}
	\Delta _{c d} = \widetilde{f} \del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu} ,
\end{equation}
where the function $\widetilde{f}$ is given by a contribution from the pullback of the metric and from the Kalb-Ramond field
\begin{multline} \label{eqn:1/f-KR}
	\frac{1}{\widetilde{f}} = \frac{1}{g + \dfrac{k \Delta}{2}} \Bigg( \frac{k \Delta}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
	- \bigg( g + \frac{3 k \Delta}{4} \bigg) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigg) .
\end{multline}
When the equation of motion for the metric $g_{a b}$ is satisfied i.e if $g_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}$, then \eqref{eqn:1/f-KR} simplifies to
\begin{equation} \label{eqn:1/f-KR-simp}
	\frac{1}{\widetilde{f}} = - \frac{k \sqrt{\Delta}}{g + k \Delta}
\end{equation}
or alternatively
\begin{equation} \label{eqn:f-KR-simp}
	\widetilde{f} = - \frac{g + k \Delta}{k \sqrt{\Delta}} = - \sqrt{\Delta} \left( \frac{g}{k \Delta} + 1 \right) .
\end{equation}
Finally, we can then write the quantum of area 2-form $\Delta _{a b}$ in terms of the pullback of the Kalb-Ramond field $b_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu}$ as
\begin{equation} \label{eqn:QA-KR-fin}
	\Delta _{a b} = - \sqrt{\Delta} \left( \frac{g}{k \Delta} + 1 \right) b_{a b} .
\end{equation}
